---
title: "Predicting Sephora Product Ratings"
author: "Madison Martin"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Introduction 
This project aims to predict the user ratings for beauty products sold on the popular website for beauty retailer Sephora. Specifically, it aims to identify the role product attributes like brand, price, online popularity, limited edition offerings, and exclusivity have on customer satisfaction with the products. 

## Research Questions: 
**What product characteristics (if any) play a role in predicting the customer satisfaction with the product, as evidenced by the product's rating? Do limited edition products tend to have higher or lower ratings? Does interest in the product seem to correlate with higher ratings?** 


### Sourcing the Data 
This data set was sourced from the Kaggle website and uploaded by user Raghad Alharbi, which you can find at this link [here](https://www.kaggle.com/datasets/raghadalharbi/all-products-available-on-sephora-website). It was collected utilizing web scraping methods during the month of April 2020 from the Sepohra US website. 

### Download the Data 
```{r download data}
# download the product data from sephora website 
# Load the necessary libraries 
library(readr)
library(tidyr)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(knitr)

# read in csv 
sephora_df <- read_csv(file = "sephora_website_dataset.csv")
head(sephora_df)
```

### Precleaning for Analysis 
```{r precleaning}
# take out the vars we don't think we will use in the analysis 
# going to remove heavy text ones: url, instructions, ingredients 
product_df <- sephora_df %>% 
  select(- URL, - how_to_use, -ingredients) 
# view(product_df)
```

I'm already seeing that some products have a different price vs. value_price. I'm guessing these are mostly sets/kits (as you can see if you head the df), but the data documentation does not state this explicitly. I am going to make a new column for these products specifically and keep it in mind as I go through my exploratory analyses. 

```{r cleaning 2}
# add column to identify products who have a different price from the "value price" 
product_df <- product_df %>% 
  mutate(deal = ifelse(value_price - price > 0, 1, 0))
```

# Exploratory Data Analysis 

First, let's get a little bit more information about the many products in our data set. 
```{r eda basic means}
# get the average price, number of loves, and rating 
mean(product_df$price)
mean(product_df$rating)
mean(product_df$number_of_reviews) 
median(product_df$number_of_reviews)
mean(product_df$love) #number of loves of product, basically likes 
```

```{r eda top brands}
# find the brands with the most products 
product_df %>% 
  count(brand, sort = TRUE) %>% 
  head(n = 10)

# make graph for this 
product_df %>% 
  count(brand, sort = TRUE) %>% 
  head(n = 10) %>% 
  ggplot(mapping = aes(reorder(brand, -n), y = n)) +
  geom_col(colour = "purple") + 
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) + #to make it easier to read
  theme_classic() + 
  labs(
    title = "Brands with Most Products Available", 
    x = "Brand", 
    y = "Number of Products Available", 
    caption = "Source: Sephora US Website" 
  )
```

```{r eda category}
# let's see which categories have the most products represented 
product_df %>% 
  count(category, sort = TRUE) %>% 
  head(n = 10)
```

```{r popular products}
# see the most popular (loves) individual products 
most_loved <- product_df[order(product_df$love, decreasing = TRUE), ] %>% 
  head(n = 15)
kable(most_loved %>% 
            select(brand, category, name, love, rating, number_of_reviews, price))
```

```{r eda correlations}
# relationship between number of reviews and rating ? 
cor(product_df$number_of_reviews, product_df$rating)

# relationship between popularity (loves) and rating? 
cor(product_df$love, product_df$rating)

# relationship between popularity (loves) and number of reviews? 
cor(product_df$love, product_df$number_of_reviews)

# this will be useful later when we select the factors for our models, to insure independence 
```

